GBDCompare

### 2019-03-13 code/MSLT/legacy/GBDCompare.Rmd
Re-add MSLT folder. Was deleted in: 183398fdc8d691c44eae468a5165c0450be41d22

---
title: "GBDCompare"
author: "Belen Zapata Diomedi"
date: "17 April 2018"
output: html_document
---

The following graphs compare rates per one by age (5-year groups) and sex for England and Greater London.

>>>>

---
title: "GBDCompare"
author: "Belen Zapata Diomedi"
date: "17 April 2018"
output: pdf_document
---

The following graphs compare rates per one by age (5-year groups) and sex for England and Greater London for all cause mortality, all cause years lived with disability and diseases specific mortality, ylds, incidence and prevalence.

Rates are in five year age groups, as per the GBD age grouping.
